File-based localization of numerical perturbations in data analysis pipelines

### 2020-08-20 paper.tex
Update region.py script

   &        \makecell{Mean}   &  \makecell{Standard error}  & \makecell{Mean}   &  \makecell{Standard error}   \\ \midrule
  Processing time (mins)      &     106.67     &     2.68     &     nd     &     nd     \\
  Output file size (GB)       &     2.8        &     0.10     &     nd     &     nd     \\
  Number of file accesses     &     94,089      &     2,645  &     nd     &     nd     \\
  Number of processes         &     8731       &     198   &     nd     &     nd     \\
  \bottomrule
  \end{tabular}
  \end{threeparttable}
  \end{table*}
}
% All experiments were run on a machine with a 3.4GHz Intel Core i7 processor
% and 32GB memory under the CentOS7 operating system.
% The average processing time per subject was approximately 2~hours (with standard error X)
% for PreFreeSurfer and 8~hours (with standard error X) for FreeSurfer.
% The average output file size was 2.7~GB (with standard error Y) for PreFreeSurfer
% and 4.1~GB (with standard error Y) for FreeSurfer.
%\tristan{Ali, are these numbers per subject or for 20 subjects? it's an average of 20 subjects}
% For each subject, PreFreeSurfer accessed 83K files and created 7.7K processes, and FreeSurfer accessed 62K files and
% created 4K processes.

>>>>

                          & \makecell{Mean}  &  \makecell{Standard error}  & \makecell{Mean}   &  \makecell{Standard error}   \\ \midrule
  Processing time (mins)  &     106.67       &     2.68                    &     650.25        &     8.88     \\
  Output file size (GB)   &     2.8          &     0.10                    &     4.15          &     0.15     \\
  Number of file accesses &     94,089       &     2,645                   &     62,729        &     984     \\
  Number of processes     &     8731         &     198                     &     4031          &     47     \\
  \bottomrule
  \end{tabular}
  \end{threeparttable}
  \end{table*}
}
% All experiments were run on a machine with a 3.4GHz Intel Core i7 processor
% and 32GB memory under the CentOS7 operating system.
% The average processing time per subject was approximately 2~hours (with standard error X)
% for PreFreeSurfer and 8~hours (with standard error X) for FreeSurfer.
% The average output file size was 2.7~GB (with standard error Y) for PreFreeSurfer
% and 4.1~GB (with standard error Y) for FreeSurfer.
%\tristan{Ali, are these numbers per subject or for 20 subjects? it's an average of 20 subjects}
% For each subject, PreFreeSurfer accessed 83K files and created 7.7K processes, and FreeSurfer accessed 62K files and
% created 4K processes.
